SemanticPaint

### 2015-12-07 cv3d_seminar/presentation.tex
presentation + notes

\title[short title]{SemanticPaint}
\author[short presentator]{Adam Kosiorek}
\institute[CAMP]{Computer Aided Medical Procedures \\
Technische Universit\"at M\"unchen}
\date[]{10.12.2015}

@@

@@

@@

\begin{frame}
\frametitle{Streaming Random Forest}
\end{frame}

>>>>

\title[short title]{SemanticPaint}
\author[short presentator]{Adam Kosiorek}
\institute[CAMP]{Advisor: M.Eng.~Keisuke Tateno}
\date[]{10.12.2015}

@@

\begin{table}
\noindent\makebox[\linewidth]{
 \begin{tabular}{c|c|c}
  Who & What & How \\ \hline
  Levoy et. al. 2000 & world-scale 3D models & offline, from online images\\ \hline
  Newcombe et. al. 2011  & online 3D scanning & KinectFusion \\ \hline
  Pradeep et.al. 2013 & 3D reconstructiona & sparse tracking and  \\
    & with 1 RGB camera  & stereo reconstruction \\
    && on par with KinectFusion
 \end{tabular}
}
\end{table}

@@

\begin{table}
\noindent\makebox[\linewidth]{
 \begin{tabular}{c|c|c}
  Who & What & How \\ \hline
  Kim et. al. 2013 & reconstruction & Voxel-based CRF \\ 
    & segmentation   & with visibility contraints\\ \hline

  Herbst et. al. 2014  & registration & online \\
     & segmentation & change detection\\ \hline

  Valentin et. al. 2013  & inference on & RGB and geom. features  \\
    & mesh from TSDF  & CRF segmentation \\
 \end{tabular}
}
\end{table}

@@

\begin{frame}
\frametitle{Random Forest}

\begin{columns}
 \begin{column}{0.5\textwidth}
  \begin{figure}
  \center
  \includegraphics[width=\textwidth]{figures/rf}
  \caption{Single tree}
\end{figure}
 \end{column}
 \begin{column}{0.5\textwidth}
    bagged trees\\
    bootstraped data\\

    voting for final result\\
    greedy training\\
    off-line, all data at once\\
    $(i, l) \in \mathcal{S}$ - (voxel, label) pairs\\
    $f(i, \theta)$ - split functions\\
    $\Theta$ - distribution of split functions\\
    $P_F(x_i = l | \mathbf{D})$\\
 \end{column}

  Information Gain:
  \begin{equation} \label{eq:infogain}
    G(S, S^L, S^R) = H(S) - \sum_{d \in \{L, R\}} \frac{|S^d|}{|S|}H(S^d)
  \end{equation}
  Shannon Entropy:
  \begin{equation}
   H(S) = - \sum_{(l, i) \in S} p(c_i = l) \log{p(c_i )}
  \end{equation}
\end{frame}
